\documentclass{scu-thesis}
 \usepackage{graphicx}	% for including graphics
% \usepackage{amsmath}	% for advanced typesetting of mathematics
% \usepackage{txfonts}	% for using the Times-Roman font
% \usepackage{natbib}	% for better citation styles

\usepackage[letterpaper, portrait, margin=1in]
{geometry}

\geometry{	
lmargin = 1.25in,
rmargin = 1.25in,
}

\usepackage{graphicx}
\graphicspath{ {images/}}

\author{Eric Beckmann}
\author{Jonathan Coon}
\author{Mikael Figueroa}
\author{Matthew Voss}
\title{A Distributed Backup System}
\department{Department of Computer Science and Engineering}
\degree{Bachelor of Computer Science and Engineering}

% These must be set first ... the rest of the thesis commands rely on them.


% Only bachelor's theses should have multiple authors and/or be from
% multiple departments.  Signatures required:
%
% Bachelor's theses: advisor(s), department chair(s)
% Master's theses: advisor, reader, department chair
% Doctoral theses: doctoral committee (including advisor), department chair

\begin{document}
\frontmatter
\signature{Ahmed Amer}
\signature{Nam Ling}

\maketitle
\include{abstract}
\include{Acknowledgements}

\tableofcontents
\listoffigures

\mainmatter
\include{introduction}
\include{Requirements}
\include{usecases}
\include{backend}
\include{designrationale}
\include{activitydiagram}
\include{testingplan}
\include{riskanalysis}
\include{timeline}
\include{societalconcerns}

%\bibliography{master}
%\bibliographystyle{ieee}

\begin{thebibliography}{9}

\bibitem{acmethics}
Acm.org, 'Code of Ethics            —                Association for Computing Machinery', 2015. [Online]. Available: http://www.acm.org/about/code-of-ethics. [Accessed: 30- Nov- 2015].

\bibitem{imagineiti}
Imagine IT, Inc., 'Biggest Backup Mistake - Minneapolis, St Paul, Edina| Imagine IT, Inc.', 2015. [Online]. Available: http://www.imagineiti.com/backup/biggest-backup-mistake. [Accessed: 30- Nov- 2015].

\bibitem{wolf}
Imgur, 'The time you spend alone with yourself.', 2015. [Online]. Available: http://imgur.com/gO8Xiot. [Accessed: 30- Nov- 2015].

\bibitem{udhr}
Un.org, 'The Universal Declaration of Human Rights | United Nations', 2015. [Online]. Available: http://www.un.org/en/universal-declaration-human-rights/. [Accessed: 30- Nov- 2015].

\bibitem{theguardian}
C.  Arthur, 'Naked celebrity hack: security experts focus on iCloud backup theory', the Guardian, 2014. [Online]. Available: http://www.theguardian.com/technology/2014/sep/01/naked-celebrity-hack-icloud-backup-jennifer-lawrence. [Accessed: 30- Nov- 2015].

\bibitem{gizmodo}
A.  Estes, 'Confirmed: NSA Paid Google, Microsoft, Others Millions for PRISM Aid', Gizmodo, 2015. [Online]. Available: http://gizmodo.com/confirmed-nsa-paid-google-microsoft-others-millions-1188615332. [Accessed: 30- Nov- 2015].

\bibitem{dropbox_fail}
A.  Ferdowsi, "Yesterday's Authentication Bug", Dropbox Blog, 2011.

\bibitem{khaaaaan}
Khan, J.I.; Tahboub, O.Y., "Peer-to-Peer Enterprise Data Backup over a Ren Cloud," in Information Technology: New Generations (ITNG), 2011 Eighth International Conference on , vol., no., pp.959-964, 11-13 April 2011.

\bibitem{backblaze}
A.  Klein, 'The Most Reliable Hard Drive 2015', Backblaze Blog | The Life of a Cloud Backup Company, 2015. [Online]. Available: https://www.backblaze.com/blog/hard-drive-reliability-stats-for-q2-2015/. [Accessed: 30- Nov- 2015].

\bibitem{independent}
M.  Landi, 'Stars' nude photo attack may have been down to password codes - Independent.ie', Independent.ie, 2014. [Online]. Available: http://www.independent.ie/business/technology/news/stars-nude-photo-attack-may-have-been-down-to-password-codes-30552629.html. [Accessed: 30- Nov- 2015].

\bibitem{hp}
M.  Lillibridge, S.  Elnikety, A.  Birrell and M.  Burrows, "A Cooperative Internet Backup Scheme", Usenix, 2003.

\bibitem{gigaom}
O.  Malik, 'S3 Outage Highlights Fragility of Web Services', Gigaom.com, 2008. [Online]. Available: https://gigaom.com/2008/07/20/amazon-s3-outage-july-2008/. [Accessed: 30- Nov- 2015].

\bibitem{scalable}
S.  Ratnasamy, P.  Francis, M.  Handley, R.  Karp and S.  Schenker, "A scalable content-addressable network", ACM SIGCOMM Computer Communication Review, vol. 31, no. 4, pp. 161-172, 2001.

\bibitem{multiagent}
Shibakawa, M.; Uchiya, T.; Takumi, I.; Kinoshita, T., "Design and implementation of multiagent-based distributed backup system," in Computer and Information Science (ICIS), 2013 IEEE/ACIS 12th International Conference on , vol., no., pp.235-240, 16-20 June 2013.


\bibitem{pepperdine}
D.  Smith, 'The Cost of Lost Data', Graziadio Business Review, vol. 6, no. 3, 2003.

\bibitem{password}
Taneski, V.; Hericko, M.; Brumen, B., "Password security — No change in 35 years?," in Information and Communication Technology, Electronics and Microelectronics (MIPRO), 2014 37th International Convention on , vol., no., pp.1360-1365, 26-30 May 2014.

\bibitem{uchiya}
Uchiya, T.; Shibakawa, M.; Takumi, I.; Kinoshita, T., "Multiagent-based distributed backup system for individuals," in Computer and Information Science (ICIS), 2015 IEEE/ACIS 14th International Conference on , vol., no., pp.361-366, June 28 2015-July 1 2015.

\bibitem{rightscale}
T.  Von Eicken, 'Amazon EC2 Outage: Summary and Lessons Learned', Rightscale.com, 2011. [Online]. Available: http://www.rightscale.com/blog/cloud-industry-insights/amazon-ec2-outage-summary-and-lessons-learned/. [Accessed: 30- Nov- 2015].

\bibitem{syncthing}
Available: https://syncthing.net/.

\bibitem{crashplan}
Available: http://www.code42.com/crashplan/.

\end{thebibliography}

\backmatter
\end{document}
