\chapter{Societal Issues}

\section{Ethical Discussion, Social Concerns, and Compassion}

\subsection{Justification}
	There are many ethical justifications for our project.  In the larger sense, we hope to make the world a better place by providing a better data backup and restore service than what is currently out there.  The bottom line is that our product will provide a convenience to the general public and assist them with storing files and also protecting against the problems of data loss.  Specifically we will help corporations become more efficient in their operations, which could bring economic prosperity and higher standards of living for society as a whole.  This is all in agreement with the first rule of the ACM Code of Ethics to ''contribute to society and human well-being.'' \cite{acmethics}

	Our project also deals directly with the human right to privacy.  As detailed in rule 1.7 of the ACM code of ethics, we are to ''respect the privacy of others.'' \cite{acmethics}  Furthermore, privacy is listed as a fundamental human right in Article 12 of the Universal Declaration in Human Rights: ''no one shall be subjected to arbitrary interference with his privacy.'' \cite{udhr}  The right to privacy is an inalienable human dignity that we hope to protect.  Privacy is so important because it gives people greater freedom to make their own moral decisions, independent from the judgement of others and shielded from the pressure to conform to their culture.  As an anonymous adage goes: ''The time you spend alone with yourself is the most precious time you have.  This is your proving ground.  It’s where you decide who you are, what values you uphold, and ultimately how you are seen in the eyes of yourself and others.'' \cite{wolf}

	The right to privacy is especially pertinent in this day and age, where more and more of everyone’s personal data is being put out online, vulnerable to access by malicious parties.  We hope our service will allow people to protect their privacy, since instead of storing their data in a single corporation’s database, which presupposes full trust in that corporation, and also provides a single point of attack for governments or hackers who wish to seize the data, we will be distributing the encrypted data securely to many locations in separate fragments.  These are not merely hypothetical concerns.  Data stores run by single entities have suffered data breaches many times in the past.  For example, Apple iCloud was hacked in August of 2014, which resulted in many celebrity photographs being leaked. \cite{independent}  Furthermore, the NSA has controversially forced companies like Google and Yahoo to turn over customer data in moves that have widely been called unconstitutional. \cite{gizmodo}  Our system will not be vulnerable to privacy violations like this, because there will no longer be a single party attackers can go after to view people's data.

\subsection{Lifelong Learning}

	Throughout this project, it was also very important that we were mindful of our own growth in moral character and technical skill.  Our society is increasingly dependent on computers, so as computer engineers we have a large role for improving people’s daily lives.  Throughout the course of this project, we made sure to adhere to the Software Engineering code of ethics.  We made every effort to put the public interests and the common good first.  And we strove for the highest quality work in all aspects.  We also strove to cultivate our own character, skills, and abilities, and will seek to grow as much as possible through this project.  Finally, sought to treat each other with respect during this project.

\subsection{Possible Pitfalls}
	As with most engineering projects, there are certain moral pitfalls that we encountered along the way.  First of all, we had to consider that potential users of our system are trusting us to keep their data as private as possible.  If we had taken any shortcuts or made any oversights while designing our system, we could have left security holes that would compromise privacy.  By not keeping people's data private, we would have exposed them to malicious parties such as identity thieves, hackers, fraud artists, and so on.  We would be indirectly responsible for any damage caused, because we made people believe they had privacy which they did not.  And this would break article 1.7 of the ACM Code of Ethics to ''Avoid harm to others''. \cite{acmethics}  It was therefore our duty to ensure privacy in our system to the maximum extent possible.

	There was also the possible pitfall of our system being used by criminals, due to the enhanced privacy it provides.  By providing a system by which users can store their data with complete privacy, we could allow criminals to hide evidence of their activities, obstructing the activities of legitimate law enforcement agencies. The peer-to-peer architecture we use is similar to protocols such as BitTorrent which are far and wide used only for illicit purposes.  Even though it is not our intention that our system would be used for illegal activities, we must consider this possibility.  Nevertheless, we believe that the net good of our system in terms of protecting people's data and right to privacy outweighs the downsides of it being used by criminals, who already hide their data through other means anyways.

\section{Political Concerns}
	This is not a public project, so we can mostly disregard political concerns.

\section{Economic considerations and Manufacturability}
	The scope of the project at this stage is not to deploy a large scale product for the public to use, but rather to make a system for the purposes of testing new algorithms and methods of data distribution.  Therefore, we will not consider the costs of deploying a final product at this time.

	As for the costs of prototyping itself, it was quite low and negligible.  The software development cost little to no resources.  We used a number of Raspberry Pi boards to implement our system.  At the cost of \$40 per board, the total cost of the project was \$160.  We supported this project with our own personal funds.

\section{Health and Safety}
	This project did not require the use of any heavy machinery, extraordinarily large power sources, etc.  Therefore, we didn't need any special safety considerations for this project.  However, we did use electronic equipment such as PCs and Raspberry Pis in the course of this project, and so we exercised common sense as we would handling any electronic appliance.

\section{Sustainability and Environmental Impact}
	The environmental impact of creating our starting system should be minimal, since it is quite small scale and only uses a few electronic devices.  For the reasons mentioned above we will not yet consider the costs of deployment for a large scale system.

\section{Usability}
	One of the requirements and goals for our system was to make our interface as user-friendly as possible.  We did this by only providing our user with a basic set of controls, hiding the complexity of the data distribution algorithm from them.

	It was also important that our system be easy to set up as well.  Currently, our system is transferred to various client machines by copying over executable and configuration files and then ensuring that that machine has the proper libraries installed as well as the correct firewall settings.  This is not the easiest to use setup method, and in future iterations of this project this is an area of improvement.  For example we could develop a good installer as well as utilize auto-configuration to the fullest extent.